Measurement and Analysis of Child Pornography Trafficking on P2P Networks\nocite{Hurley}

### 2013-10-16 Paper_presentation.tex
Corrigido duplicidade

\item[\checkmark] Random.
\item[\checkmark] Number of days observed. 
\item[\checkmark] Corpus size.
\item[\checkmark] Contribution to file availability on Gnutella and eMule.
\item[\checkmark] 10 or fewer FOI.
\item[\checkmark] Peers in the U.S.

@@

\begin{frame}
\begin{block}{Impact of Low-Sharing GUIDs on Availability}
\begin{itemize}
\item[\checkmark] A large portion of GUIDs have comparatively few files. 
\item[\checkmark] Reasons peers may appear to have few files.
\begin{itemize}
\item[\checkmark] They may be downloading FOI and not subsequently sharing them.
\item[\checkmark] They may have downloaded the files incidental to other activities.
\item[\checkmark] They may have downloaded the files incidental to other activities.
\item[\checkmark] They may simply be sharing a smaller library.
\end{itemize}

\end{itemize}
\end{block}
\end{frame}
\begin{frame}
\begin{block}{Files in Corpus}
\begin{itemize}
\item[\checkmark] CDF showing the corpus size per GUID.
\begin{itemize}
\item[\checkmark] The blue line show all FOI observed in Gnutella.
\item[\checkmark] The black line (“Gnutella Browse GUIDs”) show the corpus size distribution for all files seen at GUIDs whose libraries were browsed.
\item[\checkmark] The green line shows the distribution of FOIs within those browses.
\item[\checkmark] The red line show all FOI observed in eMulle.
\end{itemize}
\end{itemize}

>>>>

\item Random.
\item Number of days observed. 
\item Corpus size.
\item Contribution to file availability on Gnutella and eMule.
\item 10 or fewer FOI.
\item Peers in the U.S.

@@

\begin{frame}
\begin{block}{Impact of Low-Sharing GUIDs on Availability}
\begin{itemize}
\item[\checkmark] A large portion of GUIDs have comparatively few files. 
\item[\checkmark] Reasons peers may appear to have few files.
\begin{itemize}
\item They may be downloading FOI and not subsequently sharing them.
\item They may have downloaded the files incidental to other activities.
\item They may simply be sharing a smaller library.
\end{itemize}

\end{itemize}
\end{block}
\end{frame}
\begin{frame}
\begin{block}{Files in Corpus}
\begin{itemize}
\item[\checkmark] CDF showing the corpus size per GUID.
\begin{itemize}
\item The blue line show all FOI observed in Gnutella.
\item The black line (“Gnutella Browse GUIDs”) show the corpus size distribution for all files seen at GUIDs whose libraries were browsed.
\item The green line shows the distribution of FOIs within those browses.
\item The red line show all FOI observed in eMulle.
\end{itemize}
\end{itemize}
